`r params$doc_title`

### 2022-11-16 scripts/MSc.Rmd
edited Msc script

```{r simulatesimulatesimulate}
## try starting with n=50.000 -> selected 9 IVs
set.seed(1234)

## initialize
nsim <- 100
se_update_BMI <- c()
se_update_GBC <- c()

est <- tibble(no_sim = 1:nsim)
#est <- matrix(NA, 
#              nrow = nsim, 
#              ncol = 2*length(n)  # theta_sim and theta_se_sim
#              ) 
#colnames(est) <- c(paste0("theta_sim_", n), paste0("theta_se_sim_", n))

## START SIM
T0 = proc.time()[3]
for (i in 1:length(colnames_pval)) {
  T0 = proc.time()[3]
  threshold <- 5*10^-6
  numIV <- sum(my_data_harm[[colnames_pval[i]]] < threshold)
  if (numIV<5) { # start with 5 IVs only (sample size ~50,000)
    next
  }

@@

    # PERFORM MR_analysis
    mr.obj = MendelianRandomization::mr_input(
          bx = sim_dat$beta.bmi_sim_norm, 
          bxse = sim_dat$se_update_BMI, 
          # outcome
          by = sim_dat$beta.gbc_sim_norm, 
          byse = sim_dat$se_update_GBC, 
          snps = sim_dat$SNP,
          exposure = "Body mass index",
          outcome = "Gallbladder Cancer"
        ) 
    # CONMIX (as reference)
    res = MendelianRandomization::mr_conmix(mr.obj)
    colname_theta <- paste0("theta_sim_", n[i])
    colname_theta_se <- paste0("theta_se_sim_", n[i])
    ## store results
    est[k, colname_theta] <- res$Estimate
    CIlength = res$CIUpper-res$CILower
    if (length(CIlength)>1) print("conmix multimodal")
    est[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
    rm(res)
  }
  print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}
T1 = proc.time()[3]
timediff = T1-T0
```

>>>>

```{r simulatesimulatesimulate, warning=FALSE}
# try starting with n=50.000 -> selected 9 IVs
set.seed(1234)

## initialize
nsim <- 25
est <- tibble(no_sim = 1:nsim)
#est <- matrix(NA, 
#              nrow = nsim, 
#              ncol = 2*length(n)  # theta_sim and theta_se_sim
#              ) 
#colnames(est) <- c(paste0("theta_sim_", n), paste0("theta_se_sim_", n))

## START SIM
T0 = proc.time()[3]
for (i in 1:length(colnames_pval)) {
 threshold <- 5*10^-6
 se_update_BMI <- c()
 se_update_GBC <- c()

 numIV <- sum(my_data_harm[[colnames_pval[i]]] < threshold)

 if (numIV<5) { # start with 5 IVs only (sample size ~50,000)
   next
 }

@@

   # PERFORM MR_analysis
   mr.obj = MendelianRandomization::mr_input(
         bx = sim_dat$beta.bmi_sim_norm, 
         bxse = sim_dat$se_update_BMI, 
         # outcome
         by = sim_dat$beta.gbc_sim_norm, 
         byse = sim_dat$se_update_GBC, 
         snps = sim_dat$SNP,
         exposure = "Body mass index",
         outcome = "Gallbladder Cancer"
       ) 
   # CONMIX (as reference)
   res = MendelianRandomization::mr_conmix(mr.obj)
   colname_theta <- paste0("theta_sim_", n[i])
   colname_theta_se <- paste0("theta_se_sim_", n[i])
   ## store results
   est[k, colname_theta] <- res$Estimate
   CIlength = res$CIUpper-res$CILower
   if (length(CIlength)>1) print("conmix multimodal")
   est[k, colname_theta_se] <- sum(CIlength)/1.96/2  ## Caution: this may be problematic 
   rm(res)
 }
 rm(se_update_BMI, se_update_GBC)
 print(paste0("|||-----------------------Run finished for sample size: ", n[i], " -----------------------|||"))
}

T1 = proc.time()[3]
timediff = T1-T0

saveRDS(est, paste0(Sys.Date(), "_est.rds"))
```
